\section{Sustainability and Scalability}

Sustainability has already been demonstrated by CodeDay, which has been operating since 2009, and Mentors in Tech, which is operating in its fourth academic year.  At scale, long-term sustainability will come from four sources, which will be developed as part of this project:

\begin{itemize}
    \item Partner colleges have been contributing to part of the operating costs for similar programs operated by CodeDay and MinT by re-purposing existing and new internal funding sources.
    
    \item Public and private-based grant funding in the near future, as the partner colleges and diverse nontraditional student populations served are severely underfunded compared to their traditional public and private counterparts. Both organizations have shown successful proposals to fund one-off program enhancements, scale, and development so far. Multi-year grants that can ensure long-term program planning and implementation will build a foundation for sustainability post-grant funding.
    
    \item Earned revenue from industry partners to sponsor student program fees, capstone and micro-internship projects, as well as employer recruiting services. CodeDay and MinT have had initial success in earned revenue in these areas in the past 3 years and will continue to invest in building relationships with private and corporate partners who will ultimately benefit from having more job-ready candidates for open emerging tech and AI positions. 
    
    \item Earned revenue by extending the model and services to early career mentorship for industry partners to help with internal employee growth, development, and retention. After hiring new graduates, this is the next problem that many companies are been concerned with in order to develop their workforce.
\end{itemize}