%
% No references allowed
%
\section{Budget Justification - CodeDay}

\subsection{A. Senior Personnel}
Approximately 2 calendar person-months (\$20,000, base annual salary \$120,000) is requested each year of the project for Tyler Menezes, PI. He will be responsible for overseeing all activities related to this project, financially managing the project activities, directing the development of all program materials in collaboration with subawardees, collaborating with the evaluator to collect, analyze, and disseminate results, and building partnerships with industry to ensure the success of the project. He will deliver annual and final reports to the NSF program officer.

\subsection{B. Other Personnel}
\$28,000 per year is requested for 40\% time of a program manager (base annual salary of \$70,000), who will be responsible for screening students, recruiting mentors, matching mentors with projects, troubleshooting student participation issues, and other day-to-day program operations for the micro-internships. The remainder of the Program Manager's time will be allocated to, and funded by, other projects. This position will be hired at the beginning of the grant.

\subsection{C. Fringe Benefits}
Fringe benefits are calculated at the rate of 15\% for all full-time employees.

\subsection{D. Equipment}
No equipment is necessary.

\subsection{E. Travel}
\$3,000 of domestic travel is requested each year to support travel for PIs to the annual ExLENT conference, and for PIs and/or the evaluator to SIGCSE, FIE, or other relevant conferences.

\subsection{F. Participant Support Costs}
\$165,000 each year (total of \$495,000) is requested for student stipends. This represents a payment of \$25 per hour for each student, with an anticipated workload of 130 hours over the year between career mentorship meetings (40 hours), micro-internships (80 hours) and other cohort activities (10 hours). CodeDay will distribute stipends for all students. Total per-student support is \$3,300.

\subsection{G. Other Direct Costs}

\subsection{Consultant Services}
\$25,000 per year is requested for the external evaluator, Emilia Gan, as detailed in the ``Evaluation'' section of the proposal. As Emilia is expected to graduate with a PhD prior to the start of the project, she will be working as a consultant.

\subsubsection{Subawards}
A subaward of \$240,000 is requested for Mentors in Tech (dba MinT). The PI for this subcontract is Kevin Wang. The subcontract funds will enable MinT to develop and run a year-long career mentoring and cohort program for participating students as described in the program description. The subcontract also provides for travel and conference registrations to disseminate results. A separate cost justification for the subcontract is provided.

\subsection{I. Indirect Costs}
Indirect costs are calculated using the de minimis rate of 10\% of modified total direct costs (MTDC; base total = \$51,000 per year).