\section{Budget Justification - Mentors in Tech }

\subsection{A. Senior Personnel}
2 calendar person-months (\$30,000, base annual salary \$180,000) is requested each year of the project for Kevin Wang, Mentors in Tech PI. He will be responsible for overseeing all activities related the career mentoring elements of the proposal. Including end to end management of career mentoring plan, operations, recruiting, onboarding, training, support, and day to day management of industry mentors, and students. He will also be coordinating with partner faculty members where students attend college and CodeDay.

\subsection{C. Fringe Benefits}
Fringe benefits are calculated at the rate of 35\% for all full-time employees.

\subsection{D. Equipment}
No equipment is necessary.

\subsection{E. Travel}
\$1,100 of domestic travel is requested each year to support travel for PIs to the annual ExLENT conference, and SIGCSE, FIE, or other relevant conferences.

\subsection{F. Participant Support Costs}
CodeDay is responsible for the distribution of the student stipend and the 40 hour of mentorship is included in the budget for CodeDay and not duplicated in MinT.

\subsection{G. Other Direct Costs}
\$29,700 per year is requested for 20\% time of a program manager, who will report to and partner with Kevin on day-to-day program operations for the career mentoring program elements. The remainder of the Program Manager's time will be allocated to, and funded by, other projects.

\$4,280 is requested for industry outreach activities over the 3 years of the proposal for costs such as advertisements and materials to ensure we are able recruit industry mentors through a variety of channels.

\subsection{I. Indirect Costs}
Indirect costs are calculated using the de minimis rate of 10\% of the total direct costs in A-G.